Energy and the CES production function

### 2015-12-09 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Now fitting only 1960--2009

<<Data>>=
# Create the HistoricalData data frames
commonVars <- c("Year", "Country", "Source")
HistoricalData <- list(
  PT =  IST %>% 
    filter(Country == "PT"), 
  UK = Leeds %>% 
    filter(Country == "UK") 
)

>>>>

<<Data>>=
# Create the HistoricalData data frames
commonVars <- c("Year", "Country", "Source")
HistoricalData <- list(
  PT = IST %>% 
    filter(Country == "PT", Year <= 2009), # Ensures all fits are done on equal basis.
  UK = Leeds %>% 
    filter(Country == "UK", Year <= 2009)
)
